---
title: "README"
 md_document:
    variant: markdown_github
date: "2024-06-18"
---
#Purpose
This is the document where I will be discussing what I did for each question for the Data Science Practical Exam.
*Please Note :) I am partially colour blind and work with a colour blind scheme package in R. This may lead to my plots having strange colours (as pointed out by my mom). I don't think the colour blind scheme will interfere with the plots that I made in this prac, but I just wanted to inform you, just in case. 


```{r}
library(pacman)
p_load(tidyverse, lubridate)
list.files('Question3/code/', full.names = T, recursive = T) %>% as.list() %>% walk(~source(.))
```

#Question 1

In this section I The US Baby Names dataset is analysed. Exploratory analysis is firstly done to see what is in the data. A time-series analysis is then done followed by an Influencer analysis.


```{r}
library(tidyverse)
pacman::p_load(ggthemes)
#data prep and load
baby_names <- read_rds("C:/Users/gabyd/Desktop/DataScience/Exam/23658045/Question1/data/US_Baby_names/Baby_Names_By_US_State.rds")
charts <- read_rds("C:/Users/gabyd/Desktop/DataScience/Exam/23658045/Question1/data/US_Baby_names/charts.rds")
HBO_titles <- read_rds("C:/Users/gabyd/Desktop/DataScience/Exam/23658045/Question1/data/US_Baby_names/HBO_titles.rds")
HBO_credits <- read_rds("C:/Users/gabyd/Desktop/DataScience/Exam/23658045/Question1/data/US_Baby_names/HBO_credits.rds")

source("C:/Users/gabyd/Desktop/DataScience/Exam/23658045/Question1/code/actors_influence_b.R")
source("C:/Users/gabyd/Desktop/DataScience/Exam/23658045/Question1/code/actors_influence_g.R")
source("C:/Users/gabyd/Desktop/DataScience/Exam/23658045/Question1/code/b_top_names_history.R")
source("C:/Users/gabyd/Desktop/DataScience/Exam/23658045/Question1/code/g_top_names_history.R")
source("C:/Users/gabyd/Desktop/DataScience/Exam/23658045/Question1/code/name_trend.R")
#source("C:/Users/gabyd/Desktop/DataScience/Exam/23658045/Question1/code/spearman.R")
source("C:/Users/gabyd/Desktop/DataScience/Exam/23658045/Question1/code/top_10_plot.R")
```

```{r}
Texevier::create_template(directory = "C:/Users/gabyd/Desktop/DataScience/Exam/23658045", template_name = "Question1")
```

This code chunk summarises the data and plots the top baby names for each gender. 
```{r}
top_national_baby <- baby_names %>% 
    group_by(Name, Year, Gender) %>% 
    summarise(Total_Count_year = sum(Count)) %>% 
    arrange(Year, desc(Total_Count_year)) 
 
girls_df<- top_national_baby %>% 
    filter(Gender == "F")

boys_df <- top_national_baby %>% 
    filter(Gender == "M")

g_top <- g_top_names_history(girls_df)
b_top <- b_top_names_history(boys_df)
 
#girls plot
p <- top_10_plot(g_top, "Top 10 Girls Names over History")
p

```



```{r}
#boys plot
h <- top_10_plot(b_top, "Top 10 Boys Names over History")   
h
```
The two graphs above show the top 10 names over History.

I had some issues with the time series analysis. I attempted the spearman correlation rank, but something was wrong in the code. I still included the function I attempted the code in. 

The influence analysis, I analysed the HBO datasets to see if actors had an influence on baby names. I only wanted to do a specific subset of tv shows so I decided on tv shows in 1990-1999. I only looked at tv show actors for the top 5 tv shows in that period. I then counted how many babies were named after these actors from the period 1990-2010. I decided on that period, to see if these influences persisted. This was all done in a function and was done seperately for boys and girls. 

For girls
```{r}
lgirls <- actors_influence_g(top_national_baby, HBO_credits, HBO_titles)
lgirls
```
For boys:


```{r}
lboys <- actors_influence_b(top_national_baby, HBO_credits, HBO_titles)
lboys

```


#Question 2
For Question 2 I made direct comparisons between Coldplay and Metallica's tempo and energy over the years. I looked at the popularity of their albums as well as the duration of their songs compared to the broad Spotify song data that was provided. 

```{r}
Texevier::create_template(directory = "C:/Users/gabyd/Desktop/DataScience/Exam/23658045", template_name = "Question2")
```
The setup :

```{r}
library(tidyverse)
pacman::p_load(purr)
pacman::p_load(lubridate)
coldplay_data <- read.csv("C:/Users/gabyd/Desktop/DataScience/Exam/23658045/Question2/data/Coldplay_vs_Metallica/Coldplay.csv")
metallica_data <- read.csv("C:/Users/gabyd/Desktop/DataScience/Exam/23658045/Question2/data/Coldplay_vs_Metallica/metallica.csv")
definitions <- read_lines("C:/Users/gabyd/Desktop/DataScience/Exam/23658045/Question2/data/Coldplay_vs_Metallica/Definitions.txt")
spotify_df <- read_rds("C:/Users/gabyd/Desktop/DataScience/Exam/23658045/Question2/data/Coldplay_vs_Metallica/Broader_Spotify_Info.rds")

#some columns is not names the same
colnames(metallica_data)[2] = "album_name"
colnames(metallica_data)[3] ="duration"

source("C:/Users/gabyd/Desktop/DataScience/Exam/23658045/Question2/code/direct_comparison_album_pop_plot.R")
source("C:/Users/gabyd/Desktop/DataScience/Exam/23658045/Question2/code/direct_comparison_energy_plot.R")
source("C:/Users/gabyd/Desktop/DataScience/Exam/23658045/Question2/code/direct_comparison_tempo_plot.R")
source("C:/Users/gabyd/Desktop/DataScience/Exam/23658045/Question2/code/song_duration_plot.R")
```
I then filtered out the live performances for direct comparisons. 

```{r}
coldplay_direct_compare <- coldplay_data %>% 
    filter(!grepl("Live", name))
metallica_direct_compare <- metallica_data %>% 
    filter(!grepl("Live", name)) %>% filter(!grepl("Live", album_name))
```
I then combined the data and added a year variable using lubridate.

```{r}
#combine data
combined_df <- bind_rows(coldplay_direct_compare %>% mutate(band = "coldplay"), metallica_direct_compare %>% mutate(band = "metallica")) 

#adding a year variable from release data using lubridate package
combined_df <- combined_df %>% 
    mutate(Year = year(ymd(release_date)))
```

For the analysis, I first started with a direct comparison between Coldplay and Metallica. I first made a tempo plot to show the changes in tempo over the years for both bands. 

```{r}
#tempo plot
g <- direct_comparison_tempo_plot(combined_df)
g
```
I did the same for energy.

```{r}
#energy plot
h <- direct_comparison_energy_plot(combined_df)
h
```
For the last comparison between the two bands, I looked at the popularity of their albums over the years. I did all of the data wrangling in a function. I removed the 'Remasteres' and 'Deluxe' albums since I do not think that those albums should be takem into account when comparing the popularity of albums. 
*This plot was my take on the plot that was provided in the assignment. 


```{r}
#popularity of album plot, I removed the remastered and deluxe albums
i <- direct_comparison_album_pop_plot(combined_df)
i
```
To see the difference between Coldplay, Metallica and the broader music industry, I did a comparison using the duration of songs. 


```{r}
spotify_avg_duration <- aggregate(duration_ms ~ year, spotify_df, mean)
metallica_avg_duration <- aggregate(duration ~ Year, combined_df[combined_df$band == "metallica", ], mean)
coldplay_avg_duration <- aggregate(duration ~ Year, combined_df[combined_df$band == "coldplay", ], mean)

spotify_avg_duration_min <- spotify_avg_duration %>% 
    mutate(minutes = duration_ms/60000)
metallica_avg_duration_min <- metallica_avg_duration %>% 
    mutate(minutes = duration/60000)
coldplay_avg_duration_min <- coldplay_avg_duration %>% 
    mutate(minutes = duration/60)

avg_duration_df <- bind_rows(spotify_avg_duration_min %>% mutate(artist = "Spotify Music") %>% mutate(Year= year), 
                             metallica_avg_duration_min %>%  mutate(artist = "Metallica"), 
                             coldplay_avg_duration_min %>%  mutate(artist = "Coldplay"))


#plot 
k <- song_duration_compare(avg_duration_df)
k


```

#Question 3: Russia - Ukraine Conflict
Some insights into the Russia-Ukraine war and specifically wheter countries inside the European Union has done enough to stem the tide of the war will be given in this section. I will provide a summary of a few key bullers to discuss around the topic of country aid. This will provide viewers with intuitive and interesting insights into which countries are giving to the Ukranian cause and which aren't. 

I start by creating a folder for Questions 3. 
```{r}
Texevier::create_template(directory = "C:/Users/gabyd/Desktop/DataScience/Exam/23658045", template_name = "Question3")
```
I give insight about the Ukraine-Russia conflict in the introduction. First, I show the total bilateral contribution by country. This figure shows that the United Kingdom have the most bilateral allocations.

```{r}
alloc <- read.csv("C:/Users/gabyd/Desktop/DataScience/Exam/23658045/Question3/data/Ukraine_Aid/Financial Allocations.csv")
commit <- read.csv("C:/Users/gabyd/Desktop/DataScience/Exam/23658045/Question3/data/Ukraine_Aid/Financial Commitments.csv")
names(alloc)[2] <- 'EU'
names(alloc)[3] <- 'fin_alloc'
names(alloc)[4] <- 'hum_alloc'
names(alloc)[5] <- 'mil_alloc'
names(alloc)[6] <- 'tot_bil_alloc'
names(alloc)[7] <- 'EU_share_alloc'
g <- 
    Contribution_by_country_plot(alloc)
g
```


#Question 4
I start by creating a folder for Question 4. 
```{r}
Texevier::create_template(directory = "C:/Users/gabyd/Desktop/DataScience/Exam/23658045", template_name = "Question4")

```
A brief introduction to the question is then given. I load the data and then adjust for the team sports that get more than one medal, but only one medal is counted for the country. This is done in a function, where I sum over the medal counter while grouping over the other variables. If the medal counter is more than one, it creates a boolean indicating that it is a team sport, or not. Thereafter, the medal counter is set to 1. 

```{r}
#loading the data
summer_data <- read_rds("C:/Users/gabyd/Desktop/DataScience/Exam/23658045/Question4/data/olympics/summer.rds")
winter_data <- read_rds("C:/Users/gabyd/Desktop/DataScience/Exam/23658045/Question4/data/olympics/winter.rds")
GDP_data <- read_rds("C:/Users/gabyd/Desktop/DataScience/Exam/23658045/Question4/data/olympics/GDP.rds")


#adjusting the data for team sports
summer_df <- adj_data_team(summer_data)
winter_df <- adj_data_team(winter_data)
```
Next I compare India's performance with other emerging economies and a selected few South American countries. I do this by first creating a dataframe with just the country and medals per country. I merge this dataframe with the GDP dataframe and create a variable for medals per capita to make comparisons easier. I choose the emerging markets and South American countries. Finally, the function 'compare plot' is used to show the past performance of the chosen countries, the medals per Capita and medals per GDP. All three plots are shown on one picture.


```{r}
summer_medals_country_df <- medals_per_country(summer_df) #this is now a data frame with just the country and total medals per country
#merged dataset with medals and gdp
merged_medals_gdp_df <- merged_medals_gdp(summer_medals_country_df, GDP_data) 
colnames(merged_medals_gdp_df)[6] = "GDP_per_Capita"


merged_medals_gdp_df<- merged_medals_gdp_df %>% 
    mutate(medals_per_capita = team_medals/Population, medals_per_gdp = team_medals/ (GDP_per_Capita) * Population)
#emerging markets: brazil, south africa, china, mexico, indonesia, add south american countries too
compare_countries <- c("BRA", "RSA", "CHN", "MEX", "INA", "IND", "ARG", "PER", "CHI")

g<- compare_plot(merged_medals_gdp_df, compare_countries)
g
```
The next question I answer is which countries have been the most dominant in both winter and summer olympics. I do this by firstly summarising the amount of medals won by year and country. I arrange the dataframes to make it possible to take the first 5 observations as the best performing countries. I do this seperately for winter and summer olympics. A function is used to plot both the results for the summer and winter olympics. 


```{r}
#summarize medals by year and country
sum_medals_year_country_df <- medals_per_year_country(summer_df)
win_medals_year_country_df <- medals_per_year_country(winter_df)

#top countries: summer
sum_top_df <- sum_medals_year_country_df %>%  group_by(Year, Country) %>% 
    arrange(Year, desc(team_medals)) %>% 
    select(Year, Country, team_medals)
top_5_year_summer_df <- sum_top_df %>%
  group_by(Year) %>%
  slice_max(order_by = team_medals, n = 5) %>%
  ungroup()


#top countries: winter
win_top_df <- win_medals_year_country_df %>%  group_by(Year, Country) %>% 
    arrange(Year, desc(team_medals)) %>% 
    select(Year, Country, team_medals)
top_5_year_winter_df <- win_top_df %>%
  group_by(Year) %>%
  slice_max(order_by = team_medals, n = 5) %>%
  ungroup()

#plot time series for both summer and winter
g<- top_countries_plot(top_5_year_winter_df, Title = "Top 5 Countries in Winter Olympics Over Time")
g

```


```{r}
h <- top_countries_plot(top_5_year_summer_df, Title = "Top 5 Countries in Summer Olympics Over Time")
h
```
The question: Which countries best punch above their weight when it comes to winning medals (however
you define this)?
I interpreted this question as realistic as possible. I decided to look at which countries perform well in boxing. 
I first create a boxing dataframe by filtering the summer olympics data to just boxing data. I then use a function to plot the results. 

```{r}
#filter for boxing
boxing_df <- summer_data %>% 
    filter(Sport == "Boxing")

boxing <- medals_per_country(boxing_df) %>% 
    arrange(desc(team_medals)) %>% 
    head(20)

w <- plot_sport(boxing, "Total Medals for Boxing")
w
```
For the last question in this section, I decided to plot which countries have won medals for football at the Summer Olympics using a world map. I downloaded the world map package. I used the following webpage (https://warin.ca/posts/rcourse-datavisualizationwithr-maps/) to understand how to create this map plot. I wanted to reference the webpage, but everytime I include a reference, the script didn't want to knit, so I decided to just mention it here. 
All of the data wrangling and plotting for this map plot was done in a function. 


```{r}
map_plot <- football_map_world(summer_df, "Countries That Have Won Medals for Football at the Summer Olympics")
map_plot
```


#Question 5: SQL
In this section I share my views on local inflation by constructing a Braaibroodjie index over a three-year period. The index contains data for white bread, cheddar, margarine, tomatoes, onions, salt and chutney. 


```{r}

Texevier::create_template(directory = "C:/Users/gabyd/Desktop/DataScience/Exam/23658045", template_name = "Question5")

```









