---
# IMPORTANT: Change settings here, but DO NOT change the spacing.
# Remove comments and add values where applicable.
# The descriptions below should be self-explanatory

title: "Coldplay vs. Metallica: A musical Journey"
#subtitle: "This will appear as Right Header"

documentclass: "elsarticle"

# --------- Thesis title (Optional - set to FALSE by default).
# You can move the details below around as you please.
Thesis_FP: FALSE
# Entry1: "An unbelievable study with a title spanning multiple lines."
# Entry2: "\\textbf{Some Guy}" # textbf for bold
# Entry3: "A thesis submitted toward the degree of Doctor of Philosophy"
# Uni_Logo: Tex/Logo.png # Place a logo in the indicated location (from your root, e.g. defaults to ~/Tex/Logo.png) and uncomment this line. Leave uncommented for no image
# Logo_width: 0.3 # If using a logo - use this to set width (size) of image
# Entry4: "Under the supervision of: \\vfill Prof. Joe Smith and Dr. Frank Smith"
# Entry5: "Stellenbosch University"
# Entry6: April 2020
# Entry7:
# Entry8:

# --------- Front Page
# Comment: ----- Follow this pattern for up to 5 authors
AddTitle: TRUE # Use FALSE when submitting to peer reviewed platform. This will remove author names.
Author1: "Gaby Jacobs"  # First Author - note the thanks message displayed as an italic footnote of first page.
Ref1: "Stellenbosch University, Stellenbosch, South Africa" # First Author's Affiliation
Email1: "23658045@sun.ac.za" # First Author's Email address


CorrespAuthor_1: TRUE  # If corresponding author is author 3, e.g., use CorrespAuthor_3: TRUE

# Comment out below to remove both. JEL Codes only given if keywords also given.
keywords: "Multivariate GARCH \\sep Kalman Filter \\sep Copula" # Use \\sep to separate
JELCodes: "L250 \\sep L100"

# ----- Manage headers and footers:
#BottomLFooter: $Title$
#BottomCFooter:
#TopLHeader: \leftmark # Adds section name at topleft. Remove comment to add it.
BottomRFooter: "\\footnotesize Page \\thepage" # Add a '#' before this line to remove footer.
addtoprule: TRUE
addfootrule: TRUE               # Use if footers added. Add '#' to remove line.

# --------- page margins:
margin: 2.3 # Sides
bottom: 2 # bottom
top: 2.5 # Top
HardSet_layout: TRUE # Hard-set the spacing of words in your document. This will stop LaTeX squashing text to fit on pages, e.g.
# This is done by hard-setting the spacing dimensions. Set to FALSE if you want LaTeX to optimize this for your paper.

# --------- Line numbers
linenumbers: FALSE # Used when submitting to journal

# ---------- References settings:
# You can download cls format here: https://www.zotero.org/ - simply search for your institution. You can also edit and save cls formats here: https://editor.citationstyles.org/about/
# Hit download, store it in Tex/ folder, and change reference below - easy.
bibliography: Tex/ref.bib       # Do not edit: Keep this naming convention and location.
csl: Tex/harvard-stellenbosch-university.csl # referencing format used.
# By default, the bibliography only displays the cited references. If you want to change this, you can comment out one of the following:
#nocite: '@*' # Add all items in bibliography, whether cited or not
# nocite: |  # add specific references that aren't cited
#  @grinold2000
#  @Someoneelse2010

# ---------- General:
RemovePreprintSubmittedTo: TRUE  # Removes the 'preprint submitted to...' at bottom of titlepage
Journal: "Journal of Finance"   # Journal that the paper will be submitting to, if RemovePreprintSubmittedTo is set to TRUE.
toc: FALSE                       # Add a table of contents
numbersections: TRUE             # Should sections (and thus figures and tables) be numbered?
fontsize: 11pt                  # Set fontsize
linestretch: 1.2                # Set distance between lines.
link-citations: TRUE            # This creates dynamic links to the papers in reference list.

### Adding additional latex packages:
# header-includes:
#    - \usepackage{colortbl} # Add additional packages here.

output:
  pdf_document:
    keep_tex: TRUE
    template: Tex/TexDefault.txt
    fig_width: 3.5 # Adjust default figure sizes. This can also be done in the chunks of the text.
    fig_height: 3.5
abstract: |
  In this Question, I will report on the longevity and musical prgression of Coldplay and Metallica. 
---

<!-- First: Set your default preferences for chunk options: -->

<!-- If you want a chunk's code to be printed, set echo = TRUE. message = FALSE stops R printing ugly package loading details in your final paper too. I also suggest setting warning = FALSE and checking for warnings in R, else you might find ugly warnings in your paper. -->

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, message = FALSE, warning = FALSE, fig.width = 6, fig.height = 5, fig.pos="H", fig.pos = 'H')
# Note: Include = FALSE implies the code is executed, but not printed in your pdf.
# warning and message = FALSE implies ugly messages and warnings are removed from your pdf.
# These should be picked up when you execute the command chunks (code sections below) in your rmd, not printed in your paper!

# Lets load in example data, and see how this can be stored and later called from your 'data' folder.
#if(!require("tidyverse")) install.packages("tidyverse")
library(tidyverse)
pacman::p_load(purr)
pacman::p_load(lubridate)
coldplay_data <- read.csv("C:/Users/gabyd/Desktop/DataScience/Exam/23658045/Question2/data/Coldplay_vs_Metallica/Coldplay.csv")
metallica_data <- read.csv("C:/Users/gabyd/Desktop/DataScience/Exam/23658045/Question2/data/Coldplay_vs_Metallica/metallica.csv")
definitions <- read_lines("C:/Users/gabyd/Desktop/DataScience/Exam/23658045/Question2/data/Coldplay_vs_Metallica/Definitions.txt")
spotify_df <- read_rds("C:/Users/gabyd/Desktop/DataScience/Exam/23658045/Question2/data/Coldplay_vs_Metallica/Broader_Spotify_Info.rds")

#some columns is not names the same
colnames(metallica_data)[2] = "album_name"
colnames(metallica_data)[3] ="duration"

source("C:/Users/gabyd/Desktop/DataScience/Exam/23658045/Question2/code/direct_comparison_album_pop_plot.R")
source("C:/Users/gabyd/Desktop/DataScience/Exam/23658045/Question2/code/direct_comparison_energy_plot.R")
source("C:/Users/gabyd/Desktop/DataScience/Exam/23658045/Question2/code/direct_comparison_tempo_plot.R")
source("C:/Users/gabyd/Desktop/DataScience/Exam/23658045/Question2/code/song_duration_plot.R")

```


<!-- ############################## -->
<!-- # Start Writing here: -->
<!-- ############################## -->

# Introduction \label{Introduction}
In this section I report on the longevity and musical progression of Coldplay and Metallica. 

#Data Preparation
Filter studio recording and live performances. 

```{r}

#filter out live performances for direct comparisons
coldplay_direct_compare <- coldplay_data %>% 
    filter(!grepl("Live", name))
metallica_direct_compare <- metallica_data %>% 
    filter(!grepl("Live", name)) %>% filter(!grepl("Live", album_name))

#combine data
combined_df <- bind_rows(coldplay_direct_compare %>% mutate(band = "coldplay"), metallica_direct_compare %>% mutate(band = "metallica")) 

#adding a year variable from release data using lubridate package
combined_df <- combined_df %>% 
    mutate(Year = year(ymd(release_date)))



```


#Analysis
In this section I look at the direct comparisons of Coldplay and Metallica. I first look at the direct comparison of the average tempo of songs by band over the years. Figure * shows that the tempo for both Coldplay and Metallica varied a lot over the years. 

```{r}
#tempo plot
g <- direct_comparison_tempo_plot(combined_df)
g
```
Next, I look at the direct comparison of energy over  time. Figure * shows that Metallica's energy has always been higher than Coldplay's. Neither bands' energy changed drastically over the years. 


```{r}
#energy plot
h <- direct_comparison_energy_plot(combined_df)
h
```
For the last direct comparison, I look at the popularity of the albums of both Coldplay and Metallica. As seen in the figure Coldplay(red) and Metallica (blue) have popular albums. However, I would say that the figure shows that Coldplay has more popular albums. 


```{r}
#popularity of album plot, I removed the remastered and deluxe albums
i <- direct_comparison_album_pop_plot(combined_df)
i
```

#Broader Context Analysis
For this section I integrate the spotify file and do a more broad analysis. 

```{r}
spotify_avg_duration <- aggregate(duration_ms ~ year, spotify_df, mean)
metallica_avg_duration <- aggregate(duration ~ Year, combined_df[combined_df$band == "metallica", ], mean)
coldplay_avg_duration <- aggregate(duration ~ Year, combined_df[combined_df$band == "coldplay", ], mean)

spotify_avg_duration_min <- spotify_avg_duration %>% 
    mutate(minutes = duration_ms/60000)
metallica_avg_duration_min <- metallica_avg_duration %>% 
    mutate(minutes = duration/60000)
coldplay_avg_duration_min <- coldplay_avg_duration %>% 
    mutate(minutes = duration/60)


avg_duration_df <- bind_rows(spotify_avg_duration_min %>% mutate(artist = "Spotify Music") %>% mutate(Year= year), 
                             metallica_avg_duration_min %>%  mutate(artist = "Metallica"), 
                             coldplay_avg_duration_min %>%  mutate(artist = "Coldplay"))


#plot 
k <- song_duration_compare(avg_duration_df)
k

```
The Figure shows the duration of songs for Coldplay, Metallica and the broader Spotify Music. Coldplay has a right skewed distribution meaning that most of their songs are shorter than Metallicas (as seen on figure). Metallica has quite a normal distribution, with majority of their songs being around 5-6 minutes. Most of the broader Spotify songs peak around 4 minutes which is similar to Coldplay's song duration. 



