---
# IMPORTANT: Change settings here, but DO NOT change the spacing.
# Remove comments and add values where applicable.
# The descriptions below should be self-explanatory

title: "US Baby Names"
#subtitle: "This will appear as Right Header"

documentclass: "elsarticle"

# --------- Thesis title (Optional - set to FALSE by default).
# You can move the details below around as you please.
Thesis_FP: FALSE
# Entry1: "An unbelievable study with a title spanning multiple lines."
# Entry2: "\\textbf{Some Guy}" # textbf for bold
# Entry3: "A thesis submitted toward the degree of Doctor of Philosophy"
# Uni_Logo: Tex/Logo.png # Place a logo in the indicated location (from your root, e.g. defaults to ~/Tex/Logo.png) and uncomment this line. Leave uncommented for no image
# Logo_width: 0.3 # If using a logo - use this to set width (size) of image
# Entry4: "Under the supervision of: \\vfill Prof. Joe Smith and Dr. Frank Smith"
# Entry5: "Stellenbosch University"
# Entry6: April 2020
# Entry7:
# Entry8:

# --------- Front Page
# Comment: ----- Follow this pattern for up to 5 authors
AddTitle: TRUE # Use FALSE when submitting to peer reviewed platform. This will remove author names.
Author1: "Gaby Jacobs"  # First Author - note the thanks message displayed as an italic footnote of first page.
Ref1: "Stellenbosch University, Stellenbosch, South Africa" # First Author's Affiliation
Email1: "23658045@sun.ac.za" # First Author's Email address


CorrespAuthor_1: TRUE  # If corresponding author is author 3, e.g., use CorrespAuthor_3: TRUE

# Comment out below to remove both. JEL Codes only given if keywords also given.
keywords: "Multivariate GARCH \\sep Kalman Filter \\sep Copula" # Use \\sep to separate
JELCodes: "L250 \\sep L100"

# ----- Manage headers and footers:
#BottomLFooter: $Title$
#BottomCFooter:
#TopLHeader: \leftmark # Adds section name at topleft. Remove comment to add it.
BottomRFooter: "\\footnotesize Page \\thepage" # Add a '#' before this line to remove footer.
addtoprule: TRUE
addfootrule: TRUE               # Use if footers added. Add '#' to remove line.

# --------- page margins:
margin: 2.3 # Sides
bottom: 2 # bottom
top: 2.5 # Top
HardSet_layout: TRUE # Hard-set the spacing of words in your document. This will stop LaTeX squashing text to fit on pages, e.g.
# This is done by hard-setting the spacing dimensions. Set to FALSE if you want LaTeX to optimize this for your paper.

# --------- Line numbers
linenumbers: FALSE # Used when submitting to journal

# ---------- References settings:
# You can download cls format here: https://www.zotero.org/ - simply search for your institution. You can also edit and save cls formats here: https://editor.citationstyles.org/about/
# Hit download, store it in Tex/ folder, and change reference below - easy.
bibliography: Tex/ref.bib       # Do not edit: Keep this naming convention and location.
csl: Tex/harvard-stellenbosch-university.csl # referencing format used.
# By default, the bibliography only displays the cited references. If you want to change this, you can comment out one of the following:
#nocite: '@*' # Add all items in bibliography, whether cited or not
# nocite: |  # add specific references that aren't cited
#  @grinold2000
#  @Someoneelse2010

# ---------- General:
RemovePreprintSubmittedTo: TRUE  # Removes the 'preprint submitted to...' at bottom of titlepage
Journal: "Journal of Finance"   # Journal that the paper will be submitting to, if RemovePreprintSubmittedTo is set to TRUE.
toc: FALSE                       # Add a table of contents
numbersections: TRUE             # Should sections (and thus figures and tables) be numbered?
fontsize: 11pt                  # Set fontsize
linestretch: 1.2                # Set distance between lines.
link-citations: TRUE            # This creates dynamic links to the papers in reference list.

### Adding additional latex packages:
# header-includes:
#    - \usepackage{colortbl} # Add additional packages here.

output:
  pdf_document:
    keep_tex: TRUE
    template: Tex/TexDefault.txt
    fig_width: 3.5 # Adjust default figure sizes. This can also be done in the chunks of the text.
    fig_height: 3.5
abstract: |
  The US Baby Names dataset is analysed in this report. 
---

<!-- First: Set your default preferences for chunk options: -->

<!-- If you want a chunk's code to be printed, set echo = TRUE. message = FALSE stops R printing ugly package loading details in your final paper too. I also suggest setting warning = FALSE and checking for warnings in R, else you might find ugly warnings in your paper. -->

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, message = FALSE, warning = FALSE, fig.width = 6, fig.height = 5, fig.pos="H", fig.pos = 'H')
# Note: Include = FALSE implies the code is executed, but not printed in your pdf.
# warning and message = FALSE implies ugly messages and warnings are removed from your pdf.
# These should be picked up when you execute the command chunks (code sections below) in your rmd, not printed in your paper!

library(tidyverse)
pacman::p_load(ggthemes)
#data prep and load
baby_names <- read_rds("C:/Users/gabyd/Desktop/DataScience/Exam/23658045/Question1/data/US_Baby_names/Baby_Names_By_US_State.rds")
charts <- read_rds("C:/Users/gabyd/Desktop/DataScience/Exam/23658045/Question1/data/US_Baby_names/charts.rds")
HBO_titles <- read_rds("C:/Users/gabyd/Desktop/DataScience/Exam/23658045/Question1/data/US_Baby_names/HBO_titles.rds")
HBO_credits <- read_rds("C:/Users/gabyd/Desktop/DataScience/Exam/23658045/Question1/data/US_Baby_names/HBO_credits.rds")

source("C:/Users/gabyd/Desktop/DataScience/Exam/23658045/Question1/code/actors_influence_b.R")
source("C:/Users/gabyd/Desktop/DataScience/Exam/23658045/Question1/code/actors_influence_g.R")
source("C:/Users/gabyd/Desktop/DataScience/Exam/23658045/Question1/code/b_top_names_history.R")
source("C:/Users/gabyd/Desktop/DataScience/Exam/23658045/Question1/code/g_top_names_history.R")
source("C:/Users/gabyd/Desktop/DataScience/Exam/23658045/Question1/code/name_trend.R")
#source("C:/Users/gabyd/Desktop/DataScience/Exam/23658045/Question1/code/spearman.R")
source("C:/Users/gabyd/Desktop/DataScience/Exam/23658045/Question1/code/top_10_plot.R")

```


<!-- ############################## -->
<!-- # Start Writing here: -->
<!-- ############################## -->

# Introduction \label{Introduction}
The US Baby Names dataset is analysed in this report. Exploratory analysis is firstly done to see what is in the data. A time-series analysis is then done followed by an Influencer analysis. 

#Exploratory Data Analysis
In this section I examine the overall trends in baby names over the years. 
```{r}
#summarise the top baby names by year and gender
top_national_baby <- baby_names %>% 
    group_by(Name, Year, Gender) %>% 
    summarise(Total_Count_year = sum(Count)) %>% 
    arrange(Year, desc(Total_Count_year)) 
 
girls_df<- top_national_baby %>% 
    filter(Gender == "F")

boys_df <- top_national_baby %>% 
    filter(Gender == "M")

g_top <- g_top_names_history(girls_df)
b_top <- b_top_names_history(boys_df)
 

```


```{r}
p <- top_10_plot(g_top, "Top 10 Girls Names over History")
p
```
The figure above shows that Mary was the most popular name across history for girls. 

```{r}
h <- top_10_plot(b_top, "Top 10 Boys Names over History")   
h
```
The figure above that shows the top 10 names for boys over history show that James is the most popular. John and Robert is close 2nd and 3rd now. It is interesting that the top names for boys are more closer to each other than for girls. 

#Time-Series Analysis
In this section the Spearman rank correlation of the top 25 baby names from each year with the following three years. This rank correlation is then used to analyse the persistence of name popularity over decades, especially focussing on 1990's and onwards. 


```{r}
#spearman function
#boys_df and girls_df is dataframes with names ordered from most popular to least per year

```

\newpage

#Influence Analysis
In this section I will identify names with significant popularity spikes and correlate them with cultural events such as tv shows, celebrities, artists and songs. 
I looked at the actors from the most popular tv shows in the 90's.

```{r}
lgirls <- actors_influence_g(top_national_baby, HBO_credits, HBO_titles)
lgirls
```
This figure shows there was a spike for most of the actors' names in the late 1990's. However, the influence of their names did not persist. 

```{r}

lboys <- actors_influence_b(top_national_baby, HBO_credits, HBO_titles)
lboys

```
Once again the plot for the boys is much different to the one for the girls. The figure above shows that there was not really a spike for any of the actors' names. 

Now I look at how the names performed of some interesting things that happen. 

A Royal Look at Names:

```{r}
q <- name_trend(girls_df, "Elizabeth", "Trend of the Name Elizabeth Over the Years")  
q
```




